Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-30 main.tex
Updated story

In this paper we focus on a well-behaved closed subset of
hyperproperties, where the execution traces remain in {\em lockstep}:
the traces execute identical sequences of instructions. While such
lockstep hyperproperties appear restrictive at first, they are still
of practical interest, as they will allow us to give an extensional
characterization of security policies such as taint tracking or stack
safety, which have been traditionally approached
intentionally. Moreover, this setting admits a principled treatment of
well-bracketed classification and declassification. Finally, a
fortunate side-effect is that because of the lockstep nature of the
execution traces, lockstep-hyperproperties are far easier to test than
their more general counterparts.

>>>>

In this paper we focus on a well-behaved closed subset of
hyperproperties, where the execution traces remain in {\em lockstep}:
the traces execute identical sequences of instructions.
%
This allows us to give a clean extensional characterization of taint
tracking as a noninterference property: intuitively, taint tracking is
a weak lockstep-hyperproperty that guarantees noninterference as long
as the execution traces remain in sync, but then allows for arbitrary
behavior after branching on a secret.
%
We also describe a strong version of lockstep hyperproperties, where
the security policy enforces the lockstepness. \leo{Something about
  full separation}
%
Finally, we generalize strong lockstep hyperproperties to allow for
\leo{what's the correct adjective here? principled? nested?
  restricted?}  changes to the observer clearance, and use this
generalization to characterize a novel stack safety property as
a variation of noninterference.

As it happens, lockstep hyperproperties are also significantly more
amenable to testing compared to traditional hyperproperties. Since
executions remain in lockstep, there is no possibility of \leo{missing
  bugs by never coming back down or a need to find an invariant strong
  enough to prove things}. We have implemented enforcement mechanisms
for all three policies for RISC-V and tested them.
